Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-04-18 main.tex
:pencil: Update manuscript

	Tags periodically switch between different states to perform backscatter modulation.
	For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	\begin{equation}
		\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
		\label{eq:backscatter_modulation}
	\end{equation}
	where $\alpha \in [0,1]$ models the (amplitude) harvest-backscatter efficiency at the direction of interest.
	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

@@

		Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
		\begin{align}
			I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
			 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
			 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
			 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in [0,1]$ represents the priority of the primary link.
	\end{subsection}

@@

\end{subequations}
Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $s \in \mathcal{S}$,
\begin{equation}
	\nabla_{t_{s}^\star} I^\star_{\mathrm{B}}(x;\hat{x}) = 0,
\end{equation}
which can be explicitly written as
\begin{equation}
	\sum_l P(x_l) \frac{(t_s^\star)^{N-1} e^{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l \mid \hat{x}_{l'+1})}{P(x_l \mid \hat{x}_{l'})} = 0,
	\label{eq:kkt_threshold_explicit}
\end{equation}
where $l' \equiv s \pmod L$.
According to \cite{Nguyen2020a}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
It implies the sequence $\{\log {P(x_l \mid \hat{x}_{l'+1})}/{P(x_l \mid \hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, which has at most one real solution by Descartes' rule of signs \cite{Jameson2006}.
In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
Therefore, we conclude $S = L$ and the proof is completed.
\qedsymbol
\label{ap:threshold}
\end{subsection}
\end{appendix}

>>>>

	Tags periodically switch between different states to perform backscatter modulation.
	For $M$-ary \gls{qam}, the complex constellation point $c_m \in \mathcal{C}$ maps to the reflection coefficient by \cite{Thomas2012a}
	\begin{equation}
		\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
		\label{eq:backscatter_modulation}
	\end{equation}
	where $\alpha \in [0,1]$ models the harvest-backscatter ratio at the direction of interest.
	For passive tags, $\alpha \ll 1$ is commonly assumed as the majority of the incident wave can be harvested to support tag modules \cite{Thomas2012a}.

@@

		Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
		\begin{align}
			I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
			 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
			 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
			 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in [0,1]$ represents the priority of the primary link.
	\end{subsection}
\end{section}

@@

		\end{subequations}
		Due to the strict inequality constraint \eqref{co:strict_inequality}, conditions \eqref{eq:dual_feasibility} and \eqref{eq:complementary_slackness} together imply $\mu_s^\star = 0$, $\forall s \in \mathcal{S}$.
		Besides, it is trivial to conclude $t_0^\star = 0$ for energy-based detection.
		As such, the necessary optimality conditions for problem \eqref{op:decision_threshold}, $\forall s \in \mathcal{S}$,
		\begin{equation}
			\nabla_{t_{s}^\star} I^\star_{\mathrm{B}}(x;\hat{x}) = 0,
		\end{equation}
		which can be explicitly written as, $\forall s \equiv l' \pmod L$,
		\begin{equation}
			\sum_l P(x_l) \frac{(t_s^\star)^{N-1} e^{-t_s^\star/\sigma_l^2}}{\sigma_l^{2N} (N-1)!} \log \frac{P(x_l \mid \hat{x}_{l'+1})}{P(x_l \mid \hat{x}_{l'})} = 0,
			\label{eq:kkt_threshold_explicit}
		\end{equation}

		According to \cite{He2021}, the optimal backward channel quantizer is convex and separates each pair of posterior distribution by a hyperplane.
		It implies, for a given output letter $l'$, the sequence $\{\log {P(x_l \mid \hat{x}_{l'+1})}/{P(x_l \mid \hat{x}_{l'})}\}_{l \in \mathcal{L}}$ changes sign exactly once.
		We notice the left-hand side of \eqref{eq:kkt_threshold_explicit} is a generalized Dirichlet polynomial, and by Descartes' rule of signs \cite{Jameson2006}, has at most one positive solution.
		% TODO
		In other words, starting from $t_0^\star$, each optimal decision region requires at most one additional distinct threshold, and we have $S \le L$.
		Therefore, we conclude $S = L$ and the proof is completed.
		\qedsymbol
		\label{ap:threshold}
	\end{subsection}
\end{appendix}
